Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-08 inc/photocathode/setup/setup.tex
tweaks to the methodology section of pe chapter

%Sub-nanosecond (ultrafast) pulsed laser-driven electron sources are now being employed in a wide variety of scientific studies: in particular, ultrafast electron diffraction (UED) \cite{sciaini_femtosecond_2011}, ultrafast transmission electron microscopy (UEM)\cite{king_ultrafast_2005}, and pulsed X-ray free electron lasers \cite{dowell_cathode_2010}.
The spatial quality of the sources for UEM and UED are often characterized in terms of their normalized transverse rms emittance \cite{dowell_quantum_2009,jensen_emittance_2010}; $\varepsilon_{\smallT} = \Delta p_{\smallT} \Delta x / (m c)$, where $\Delta p_{\smallT} = \sqrt{ \langle p_{\smallT}^2 \rangle }$ is the rms transverse momentum of the source and $\Delta x = \sqrt{ \langle x^2 \rangle }$  is its size (cylindrical symmetry assumed), and $m$ is the electron rest mass and $c$ is the speed of light in vacuum.
This quantity is conserved under free-space propagation and perfect lensing, but may increase due to lens aberrations \cite{oshea_reversible_1998}.
As I have discussed in Chapter \ref{chap:considerations}, an electron beam (or in the case of UEM, a pulse) with a lower transverse emittance will result in higher quality images, however since this quantity is conserved, the only chance to minimize this quantity occurs upon emission.
As a reduction in the source size $\Delta x$ is limited either by the attainable diffraction-limited incident laser pulse focusing or by the short-pulse Child's Law (screening of the electron gun's acceleration field) \cite{valfells_effects_2002}, significant improvements in the performance of scientific instruments employing pulsed electron sources through a reduction in their spatial emittance $\varepsilon_{\smallT}$ (and consequent increase in brightness \cite{berger_dc_2009}) may only be possible by decreasing the rms transverse momentum $\Delta p_{\smallT}$ of the electron source --- an intrinsic property of the emission source \cite{dowell_quantum_2009,jensen_emittance_2010}.

@@

To ensure that the transverse momentum distribution is observed, the YAG scintillator must be positioned at the back focal plane (the Fourier plane) of the lens system.
This is readily achieved by appropriate adjustment of the current $I$ in the magnetic lens coils; specifically, after determining the current required to focus the electron beam onto the scintillator, optical imaging relations together with the $I^2$ dependence of the magnetic lens strength are used to find the current that ensures that the average lens to scintillator distance equals the focal length of the lens system.
Simulation of the experimental apparatus (employing the extended AG model, see Section \ref{sec:external_forces} ), also shown in \ref{fig:transverse-measurement}, confirms that this procedure places the YAG scintillator at the back focal plane of the lens system to within a $\pm$0.5cm error.
This simulation also confirms that for our experimental conditions (less than 5,000 electrons/pulse and $\Delta x > $ 30$\mu$m) space-charge effects do not influence the observations.
Additionally, and as expected from optical considerations, the modeling shows that the spatial beam size in the Fourier plane is independent of the incident laser spot size on the photocathode (i.e., the electron source size, $\Delta x_0$).

>>>>

%Sub-nanosecond (ultrafast) pulsed laser-driven electron sources are now being employed in a wide variety of scientific studies: in particular, ultrafast electron diffraction (UED) \cite{sciaini_femtosecond_2011}, ultrafast transmission electron microscopy (UEM)\cite{king_ultrafast_2005}, and pulsed X-ray free electron lasers \cite{dowell_cathode_2010}.
The spatial quality of the sources for UEM and UED are often characterized in terms of their emitted electron beam's normalized transverse rms emittance \cite{dowell_quantum_2009,jensen_emittance_2010}; $\varepsilon_{\smallT} = \Delta p_{\smallT} \Delta x / (m c)$, where $\Delta p_{\smallT} = \sqrt{ \langle p_{\smallT}^2 \rangle }$ is the rms transverse momentum of the beam, $\Delta x = \sqrt{ \langle x^2 \rangle }$ is its size (cylindrical symmetry assumed), and $m$ is the electron rest mass and $c$ is the speed of light in vacuum.
This quantity is conserved under free-space propagation and perfect lensing, but may increase due to lens aberrations \cite{oshea_reversible_1998}.
As I have discussed in Chapter \ref{chap:considerations}, an electron beam (or in the case of UEM, a pulse) with a lower transverse emittance will result in higher quality images, however since this quantity is conserved, the only chance to minimize this quantity occurs upon emission.
As a reduction in the source size $\Delta x_0$ is limited either by the attainable diffraction-limited incident laser pulse focusing or by the short-pulse Child's Law (screening of the electron gun's acceleration field) \cite{valfells_effects_2002}, significant improvements in the performance of scientific instruments employing pulsed electron sources through a reduction in their spatial emittance $\varepsilon_{\smallT}$ (and consequent increase in brightness \cite{berger_dc_2009}) may only be possible by decreasing the initial rms transverse momentum $\Delta p_{\smallT}$ of the electron source --- an intrinsic property of the emission source \cite{dowell_quantum_2009,jensen_emittance_2010}.

@@

To ensure that the transverse momentum distribution is observed, the YAG scintillator must be positioned at the back focal plane (the Fourier plane) of the lens system.
This is readily achieved by appropriate adjustment of the current $I$ in the magnetic lens coils; specifically, after determining the current required to focus the electron beam onto the scintillator, optical imaging relations together with the $I^2$ dependence of the magnetic lens strength are used to find the current that ensures that the average lens to scintillator distance equals the focal length of the lens system.
Simulation of the experimental apparatus (employing the extended AG model, see Section \ref{sec:external_forces} ), confirms that this procedure places the YAG scintillator at the back focal plane of the lens system to within a $\pm$0.5cm error (\ref{fig:transverse-measurement}).
This simulation also confirms that for our experimental conditions (less than 5,000 electrons/pulse and $\Delta x_0 > $ 30$\mu$m) space-charge effects do not influence the observations.
Additionally, and as expected from optical considerations, the modeling shows that the spatial beam size in the Fourier plane is independent of $\Delta x_0$, the rms laser spot size incident on the photocathode (i.e., the electron source size).
